%*******************************************************
% Abstract
%*******************************************************
%\renewcommand{\abstractname}{Abstract}
\pdfbookmark[1]{Abstract}{Abstract}
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\vfill
\pdfbookmark[1]{Abstract}{Abstract}
\chapter*{Abstract}
The arena of mobile computing has changed dramatically in the past 10 years. It has advanced very rapidly, leaving behind those who couldn't keep up with the development pace and taking the innovators and visionaries for the ride of their lives.\\
\newline
Mobile Computing is not only changing the way we do business, but also the way we live and interact with our environment. It has become so common to always have a computing device with us, that the demand for useful applications has skyrocketed, thus making the development of software for these devices a very lucrative field.\\
\newline
But, \marginpar{Please note that 'the cloud' is not an \spacedlowsmallcaps{actual} cloud.} even though the devices in our pockets get more powerful year by year, very few applications rely solely on the data and computing power inside the device. The most useful applications are always connected to a magical place called \spacedlowsmallcaps{the cloud}.\\
\newline
This paper is structured in 4 parts. 


In \spacedlowsmallcaps{Part 1} we will take a brief look into the history of mobile computing itself and of the currently available platforms. We will also take a glance at the history of \emph{MHM Systemhaus GmbH}, the company that kindly gave me the opportunity to write this paper and develop a mobile application for their eRecruiting Service.   


\spacedlowsmallcaps{Part 2} will focus on the steps it takes to design a mobile application, the possibilities for multi-platform development and the challenges one has to consider when choosing the best approach and framework for cross-platform development.

In \spacedlowsmallcaps{Part 3} we will discuss what the cloud actually is and how we can optimise a service to create a seamless connection to a mobile device. We also will review the challenges one has to consider in order to effectively and securely connect an application to a cloud service.

Finally, \spacedlowsmallcaps{Part 4} will collect all of the topics previously discussed and will focus on the development of a real world application using the MHM eRecruiting System as cloud service.       


\vfill


\endgroup			

\vfill