%************************************************
\chapter{Introduction}\label{ch:introduction}
%************************************************
The arena of mobile computing has changed dramatically in the past 10 years. It has advanced very rapidly, leaving behind those who couldn't keep up with the development pace and taking the innovators and visionaries for the ride of their lives.

Mobile Computing is not only changing the way we do business, but also the way we live and interact with our environment. It has become so common to always have a computing device with us, that the demand for useful applications has skyrocketed, thus making the development of software for these devices a very lucrative field.

But, even though the devices in our pockets get more powerful year by year, very few applications rely solely on the data and computing power inside the device. The most useful applications are always connected to a magical place called \spacedlowsmallcaps{the cloud}.

But what exactly is The Cloud? In this work we will learn all about the different types of services that can run on top a cloud infrastructure and how we can communicate with these services.

And, where do mobile applications come into play? They are actually very important. The advancement in mobile technology has fueled an entire economic growth for mobile software development. Every big company out there wants to have a presence inside mobile devices, just like when the internet was booming and they wanted to have a web presence.

All this demand for mobile software solutions has been the catalyst in the development of different frameworks that can help developers create applications compatible with the different Mobile Operating Systems out there.

This particular conundrum is the main focus of this work. We will investigate and evaluate the most popular frameworks available and after we make a decision, we will get our hands dirty and dive into the creation of a multi-platform mobile application for Android and iOS, but not before we talk about the history of mobile computing and discuss the different mobile platforms currently available.

\section{Goals of this Work}

This is work part of my Bachelor's Thesis and is required for me to graduate from the University of Applied Sciences in Stuttgart, Germany and was produced in conjunction with \textit{MHM Systemhaus GmbH}. The second part is an oral presentation regarding what's being discussed here, plus a demonstration of the application that resulted from this endeavor.

The commercial goals of this work, as discussed with \textit{MHM} are:
\begin{itemize}
\item Create a multi-platform application that aggregates open job positions from different companies into a single view.
\item The application must be generic, meaning all clients of \textit{MHM} should show up and there should be a way to see only the open positions of one client.
\item There should be search functionality and past searches should be saved.
\item Notifications should be sent based on past searches.
\item Implementation of a so-called "Upload-Application", so that the user can apply to a job, directly from the app, by uploading his files.
\end{itemize}

The academic goals of this work are:
\begin{itemize}
\item Investigate how The Cloud works and understand its impact on our field of work and on society.
\item Learn about the different alternatives for the creation of a multi-platform mobile application
\item Deepen my knowledge about mobile technologies and mobile application development.
\item Learn a new Programming Language and a new way of creating mobile applications.
\end{itemize}


\section{Writing Conventions}
Newly introduced concepts that are relevant to a chapter will be described there, for all other concepts, please refer to the Glossary inside \autoref{glos}.

\spacedlowsmallcaps{Important Note:} Some things of the style used for this work might look unusual at first glance, many people feel so in the beginning.
However, all things were intentionally designed to be as they are.










   

