%************************************************
\chapter{Conclusion}\label{ch:conclusion}
%************************************************

During the past 4 months I have dived head on into the world of mobile applications, mobile development and cloud computing. It has been a marvelous adventure that has now come to an end. And as it is with the end of every experience, we should reflect on what has been achieved, the goals that were completed and the obstacles that were faced.

A very important decision was made at the beginning of this thesis. We decided to use \textit{Xamarin} for the development of our applications. I believe we made the right decision. \textit{Xamarin} has proven to be an invaluable ally in this journey, providing us with easy-to-use tools and a great community that helped me solve many of the problems I faced.

It gave me the opportunity to implement a multi-platform application in the most native way possible, by allowing me to choose which elements were done natively and which elements were shared. This flexibility not only resulted in two native looking and native performant applications, but also allowed me to deepen my knowledge of both Android and iOS programming.

At the beginning of the whole process we set ourselves with two groups of goals, an academic and a commercial one. 

Let's begin with the commercial goals.

\begin{table}[H]
    \myfloatalign
  \begin{tabularx}{\textwidth}{Xll} \toprule
    \tableheadline{Goal} & \tableheadline{Completed?}\\ 
    \midrule
    Multiplatform App & \ding{52}\\
    Generic App & \ding{52}\\
    Search Functionality & Partially\\
    Notifications & \ding{52}\\
    Upload-Apply to Jobs  & \ding{56}\\
    %\midrule
    \bottomrule
  \end{tabularx}
  \caption[Commercial Goals Achieved]{Commercial Goals Achieved}  \label{tab:com}
\end{table}

Regarding the partially completed search functionality; I unfortunately didn't have enough time to implement the ability to show the save searches as suggestions to the user in iOS. This feature was fully implemented under Android, though.

The implementation of the last goal was a little bit out of my control, since the eRecruiting Systems haven't been updated to support this feature yet. I gave it a lower priority and, due to time constraints, didn't manage to implement the skeleton for the functionality. There is however the possibility to apply to one of the jobs through the responsive web interface of the eRecruiting Application. This can be done right from the app, by clicking the "Apply Now!" button in the lower part of the single Publication view.

One of the biggest obstacles that I faced while tackling these goals, was to give the right priority to the features and to the platforms. More than once I saw myself concentrating more on the iOS application at the beginning and leaving the Android application almost unimplemented. And towards the end it was the other way around, which resulted in the Android Application looking more polished than the iOS application, even though both offer almost the same functionality.




Now for the academic goals.

\begin{table}[H]
    \myfloatalign
  \begin{tabularx}{\textwidth}{Xll} \toprule
    \tableheadline{Goal} & \tableheadline{Completed?}\\ 
    \midrule
    Understand the Cloud & \ding{52}\\
    Learn about multi-platform development & \ding{52}\\
    Improve knowledge about mobile technologies & \ding{52}\\
    Learn new Programming Language & \ding{52}\\
    %\midrule
    \bottomrule
  \end{tabularx}
  \caption[Academic Goals Achieved]{Academic Goals Achieved}  \label{tab:aca}
\end{table}

Every single task I did in order to complete this thesis or the application contributed to each and every one of these goals. All the research I did prior to starting and all the information I had to collect in order to find solutions to problems I was facing, helped make the achievement of this goals easier. The hardest part was to find the right balance between learning new stuff, programming the application and writing the thesis.

Developing an application compatible with two very different platforms has been an arduous process, requiring countless hours of preparation and investigation before I even began to develop the application. It has been a long journey, but I learned a lot more than what I expected.

I learned about the history of mobile computing and how it has affected our society, about the different mobile platforms and their peculiarities. I also learned about all the different ways there are to develop a multi-platform mobile application.

But the biggest and most important thing I learned was how to manage a software project almost entirely by myself. I had a set of defined goals and a timeline in which to do them, but other than that I received no instructions or guidance on how to proceed or how to structure my work. This endeavor has taught me discipline and patience, and has give me the confidence to know that I can achieve success in a real world environment.








